\LARGE \bf Human-Robot Interaction: A Deliberative Architecture

### 2013-07-26 paper.tex
Added a table with the main experiments carried
Used as introduction to the 'experiements' section

One classical application of this cognitive skill is the so-called
\emph{False-Belief} experiment (also known as the \emph{Sally and Ann}
experiment)~\cite{Leslie2000}: a child is asked to watch a scene where two
people, A and B, manipulate objects. Then A leaves and B hides away one
object. When A comes back, we ask the child ``where do you think A will
look for the object?''. Before acquiring a theory of mind, children are not
able to separate their own (true) model of the world (where they know that
the object was hidden) from the model of A, which contains \emph{false
beliefs} on the world (A still thinks the object is at its original
position since he did not see B hiding it). Using separate knowledge models
in the knowledge base, we have been able to replicate this experience with
our robots~\cite{Warnier2012a}.

@@

\section{Experimental results}

>>>>

One classical application of this cognitive skill is the so-called
\emph{False-Belief} experiment (also known as the \emph{Sally and Ann}
experiment)~\cite{Leslie2000}: a child is asked to watch a scene where two
people, A and B, manipulate objects. Then A leaves and B hides away one
object. When A comes back, we ask the child ``where do you think A will
look for the object?''. Before acquiring a theory of mind, children are not
able to separate their own (true) model of the world (where they know that
the object was hidden) from the model of A, which contains \emph{false
beliefs} on the world (A still thinks the object is at its original
position since he did not see B hiding it). Using separate knowledge models
in the knowledge base, we have been able to replicate this experience with
our robots~\cite{warnier2012when}.

@@

\section{Experimental outcomes}

Our architecture has been deployed and tested in a number of experiments on
several robotic platforms. Table~\ref{table|experiences} lists the most
significant ones, with their main focuses and reference publication for the
interested reader.

\begin{table*}
\begin{center}

\begin{tabular}{llll}
 \bf{Experiment} & Focus & \emph{Notes} & Reference \\
\hline
{\it Point \& Learn} (2010) & Interactive knowledge acquisition & & \cite{Lemaignan2010} \\
{\it Spy Game} (2010) & Interactive object discrimination & & \cite{Ros2010b} \\
{\it Moving to London} (2011) & Multi-modal interaction, perspective taking & \emph{immobile robot} & \cite{lemaignan2011what} \\
{\it Roboscopie} (2011) & Theater, reflection on the future of HRI & \emph{semi-autonomous} & \cite{lemaignan2012roboscopie} \\
{\it Cleaning the table} (2011) & Full integration & & \cite{Alami2011} \\
{\it I'm in your shoes} (2012) & False beliefs & & \cite{warnier2012when} \\
{\it Give me this} (2012) & Natural joint object manipulation & & \cite{gharbi2013natural} \\
{\it Aperitif time} (2012) & Multi-modal interaction, perspective taking & & \cite{lemaignan2013talking} \\
\hline

\end{tabular}
\end{center}
\caption{Main experiments conducted with our cognitive architecture.}
\label{table|experiences}
\end{table*}
